%-------------------------
% Resume Template
% Author : Orest Tokovenko
% Github : https://github.com/oresttokovenko
% License : MIT
% Type: Professional Developer
%------------------------

%-------------------------------------------------------------------------------
%                Document & Class
%-------------------------------------------------------------------------------

\documentclass[letterpaper]{resume_config}

% NOTE: <- font size adjustment is available in the resume_config.cls file on the left hand side. ex. \LoadClass[#pt]{article} where # is 10, 11 or 12

% NOTE: If you need to adjust the space between any two lines, use this function: \vspace{#pt} where # is your number. ex. \vspace{-5pt} decreases the space between lines

%-------------------------------------------------------------------------------
%                Resume Starts Here
%-------------------------------------------------------------------------------
\usepackage{xcolor}
\definecolor{light-gray}{gray}{0.95}
\newcommand{\code}[1]{\colorbox{light-gray}{\texttt{#1}}}

\begin{document}

\Header
    {Zane Dufour} % name
    {Detroit, MI} % city, province
    {310-600-8638} % phone number
    {znd4@pm.me} % email
    {zane-dufour-74023872} % https://linkedin.com/in/_______
    {znd4} % https://github.com/_______
    [znd4.github.io] % website - this parameter is optional, removing it won't impact the function's behavior

%-------------------------------------------------------------------------------
%                Work Experience
%-------------------------------------------------------------------------------

\section{Work Experience}

\WorkExperience
    {AI Senior Software Engineer} % job title
    {Volkswagen Group of America} % company name
    {June 2023 --- Present} % beginning and end of employment. If currently employed write " -- Present"
    {Remote} % city, country of employment
    {
        \item Built cloud-native ML application development platform. Deployed k8s, ArgoCD, kubeflow, and opentelemetry.
        \item Migrated docker-compose development environments to k8s using skaffold and jsonnet.
    } 

\WorkExperience
    {Senior Software Engineer, Backend} % job title
    {\href{https://www.aspiration.com/}{Aspiration}} % company name
    {January 2022 --- May 2023} % beginning and end of employment
    {Remote} % city, country of employment
    {
        \item Implemented CircleCI Orb to install and run \code{pre-commit} hooks to enforce code quality tools in CI pipelines.
        \item Introduced end-to-end tests to serverless functions using \code{sam local invoke}, ending a series of damaging incidents caused by faulty Lambda configurations being merged into \code{main} without being tested.
        \item Spearheaded wider adoption of \textit{distributed tracing} by contributing Datadog APM Twirp middleware to the org's shared middleware library.
        \item Used Snowflake to diagnose a low-probability bug that was causing some customers to be overcharged.
        \item Created Backstage onboarding workflow to streamline adoption of the new development platform.
        \item Developed customer-facing gRPC services with golang, kubernetes, terraform, and AWS Lambda.
    }

\WorkExperience
    {Tech Lead - MLOps} % job title
    {\href{https://www.ford.com/}{Ford Motor Company}} % company name
    {February 2020 --- January 2022} % beginning and end of employment
    {Dearborn, MI / Remote} % city, country of employment
    {
        \item Promoted use of modern python development tools, including \code{poetry}, \code{black}, \code{pre-commit}, and \code{tox}
        \item Mentored a growing team of 5--10 Data Scientists and Software Engineers.
        \item Designed a system to streamline the request of new pypi packages / versions, saving hundreds of labor hours. 
        \item Built a POC python SDK for Ford's ML platform.
        \item Deployed >10 ML models to production, using scikit-learn, tensorflow, datarobot, and xgboost.
        \item Wrangled data with kubernetes, pandas, dask, dagster, airflow, and argo workflows.
    }

\WorkExperience
    {Data Scientist} % job title
    {\href{https://www.ford.com/}{Ford Motor Company}} % company name
    {November 2017 --- February 2020} % beginning and end of employment
    {Dearborn, MI} % city, country of employment
    {
        \item Used pyspark / SparkML to train and score a likelihood-to-purchase model on ~100M non-customers.
        \item Converted ad-hoc notebooks into production-ready, version-controlled code.
        \item Contributed a python package to simplify the process of instantiating a pyspark driver on Ford's on-prem computing cluster.
        \item Drove adoption of test-driven-development and static code analysis for python libraries, data pipelines, and Flask services.
    }

\WorkExperience
    {Software Engineer Intern} % job title
    {\href{https://sites.disney.com/waltdisneyimagineering/}{Walt Disney Imagineering}} % company name
    {June --- September 2017} % beginning and end of employment
    {Glendale, CA} % city, country of employment
    {
        \item Contributed to \href{https://en.wikipedia.org/wiki/Projection_mapping}{projection mapping} software that is used by many attractions that are each worth over \$100M.
    }

\WorkExperience
    {Software Engineer Intern} % job title
    {\href{https://intel.com}{Intel}} % company name
    {June --- September 2017} % beginning and end of employment
    {Glendale, CA} % city, country of employment
    {
        \item Worked on desktop application used to control advanced electronics manufacturing robot.
    }
\vspace{-10pt}
%-------------------------------------------------------------------------------
%                Certifications
%-------------------------------------------------------------------------------

% \section{Certifications}

% \Certification
%     {Certified Developer - Associate} % credential name
%     {Amazon Web Services (AWS)} % issuing institution
%     {Aug 2021} % date of completion

% \vspace{-7pt}
%-------------------------------------------------------------------------------
%                Education
%-------------------------------------------------------------------------------

\section{Education}

\EducationExperience
    {University of California, Berkeley} % school name
    {BA Applied Math, BA Physics} % credential name
    {May 2017} % date of graduation
    {Berkeley, CA} % city, country of school

\vspace{-14pt}
%-------------------------------------------------------------------------------
%                Skills
%-------------------------------------------------------------------------------

\section{Skills}

\vspace{1pt}

\SkillList{
    \SkillItem{Languages}{: Python, Golang, Lua, Nix, C\texttt{++}, Rust}
    \SkillItem{Frameworks}{: flask, fastapi, twirp, typer (CLI)}
    \SkillItem{Databases}{: PostgreSQL, Hive, Snowflake}
    \SkillItem{Platforms}{: AWS, GCP, Kubernetes}
}

\end{document}

%-------------------------------------------------------------------------------
%                Resume Ends Here
%-------------------------------------------------------------------------------
